New approaches to teachers' experience of stress: Do heart rate measurements with fitness trackers provide an efficient, inexpensive, and robust measurement method?

### 2023-01-24 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd

floatsintext      : no
linenumbers       : yes
draft             : no
mask              : no

@@

@@

>>>>

floatsintext      : yes
linenumbers       : yes
draft             : no
mask              : no

@@

### Pairwaise t-test and effect size

@@

# First visual results

The graph \@ref(fig:overall_plot) show the heart rate for the entire course of the study.

```{r overall_plot, fig.height = 8, fig.width = 15}

  main %>% 
  filter(time_span == "overall") %>% 
  select("ID","time_span", "time","heart_rate") %>% 
  distinct() %>% 
  ggplot(mapping = aes(x = time,
                       y = heart_rate
                       )
         ) +
 # stat_smooth(geom = "line",
 #             method = "loess",
 #             se = FALSE) +
  geom_smooth(method = "loess",
              se = FALSE) +
  scale_color_viridis_d(option = "A",
                        end = 0.8) +
  scale_linetype_manual(values = c(1, 6)) +
  labs(x = "Time (in seconds)",
       y = "Heart rate (in beats per minute)") +
  theme_apa() -> overall_plot

overall_plot

The second graph \@ref(fig:phase_plot) show the heart rate for the individual five phases.

```{r phase_plot, fig.height = 8, fig.width = 15}

main %>% 
  filter(time_span != "overall") %>% 
  select("ID","time_span", "time","heart_rate") %>% 
  mutate(
    # status = case_when(ID < 200 ~ "Unerfahren",
    #                         ID > 200 ~ "Erfahren"),
         time_span = fct_recode(time_span,
                                "Pre-teaching phase" = "pre",
                                "Teaching phase" = "main",
                                "Post-teaching phase" = "subsequent",
                                "Intview phase" = "interview",
                                "End phase" = "after"
                                ),
         time_span = factor(time_span,
                            levels = c("Pre-teaching phase",
                                       "Teaching phase",
                                       "Post-teaching phase",
                                       "Intview phase",
                                       "End phase"
                                       )
                            )
         ) %>%
  distinct() %>% 
ggplot(mapping = aes(x = time,
                     y = heart_rate
                     )
       ) +
  geom_smooth(method = "glm") +
  scale_color_viridis_d(option = "A",
                        end = 0.8) +
  scale_linetype_manual(values = c(1, 6)) +
  labs(x = "Time (in seconds)",
       y = "Heart rate (in beats per minute)") +
  theme_apa() +
  facet_grid(cols = vars(time_span),
             scales = "free_x",
             ) -> phase_plot

phase_plot

### 2023-01-24 02_paper/02_study/02_fitbit paper/fitbit_paper.tex

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{heart rate; photoplethysmography; wearable electronic device; teaching\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

@@

We used R (Version 4.1.3; R Core Team, 2022) and the R-packages \emph{broom} (Version 1.0.1; Robinson, Hayes, \& Couch, 2022), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{DescTools} (Version 0.99.45; Andri et mult. al., 2022), \emph{dplyr} (Version 1.0.10; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{ggpubr} (Version 0.4.0; Kassambara, 2020), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{imputeTS} (Version 3.2; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.1.0; Firke, 2021), \emph{jtools} (Version 2.2.0; Long, 2022), \emph{lm.beta} (Version 1.6.2; Behrendt, 2022), \emph{lme4} (Version 1.1.30; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.5.1; Bates, Maechler, \& Jagan, 2022), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{ppcor} (Version 1.1; Kim, 2015), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.3; Wickham, Hester, \& Bryan, 2022), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2022), \emph{rstatix} (Version 0.7.0; Kassambara, 2021), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), and \emph{viridisLite} (Version 0.4.0; Garnier et al., 2021b) for all our analyses (descriptive statistics, correlations, and multilevel regression). Statistical assumptions including linearity, homogeneity of variance, and normal distribution of residuals were tested and confirmed with RStudio {[}palmeri2020{]}. An alpha level of 0.05 was used for the statistical tests.

@@

\begin{table}[h]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:descriptive statistics}Mean, SD and range for teachers' heart rate in individual phases}

\tiny{

\begin{tabular}{lllll}
\toprule
time\_span & \multicolumn{1}{c}{M heart rate in bpm} & \multicolumn{1}{c}{SD heart rate in bpm} & \multicolumn{1}{c}{Min heart rate in bpm} & \multicolumn{1}{c}{Max heart rate in bpm}\\
\midrule
after & 77.20 & 11.04 & 50.00 & 120.00\\
interview & 82.40 & 11.78 & 51.00 & 132.00\\
main & 100.28 & 16.55 & 56.00 & 164.00\\
pre & 96.21 & 14.10 & 56.00 & 139.00\\
subsequent & 94.08 & 14.28 & 63.00 & 150.00\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table}

Teachers' average heart rate during the entire course of the study was approximately 95.93 bpm with a standard deviation of 14.03 and a range from 56 to 139 bpm.

@@

@@

@@

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{heart rate; photoplethysmography; wearable electronic device; teaching\newline\indent Word count: X}
\usepackage{lineno}

@@

We used R (Version 4.1.3; R Core Team, 2022) and the R-packages \emph{broom} (Version 1.0.1; Robinson, Hayes, \& Couch, 2022), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{DescTools} (Version 0.99.45; Andri et mult. al., 2022), \emph{dplyr} (Version 1.0.10; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{ggpubr} (Version 0.4.0; Kassambara, 2020), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{imputeTS} (Version 3.2; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.1.0; Firke, 2021), \emph{jtools} (Version 2.2.0; Long, 2022), \emph{lm.beta} (Version 1.6.2; Behrendt, 2022), \emph{lme4} (Version 1.1.30; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.5.1; Bates, Maechler, \& Jagan, 2022), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{ppcor} (Version 1.1; Kim, 2015), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.3; Wickham, Hester, \& Bryan, 2022), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2022), \emph{rstatix} (Version 0.7.0; Kassambara, 2021), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.1; Garnier et al., 2021b), and \emph{xfun} (Version 0.36; Xie, 2022) for all our analyses (descriptive statistics, correlations, and multilevel regression). Statistical assumptions including linearity, homogeneity of variance, and normal distribution of residuals were tested and confirmed with RStudio {[}palmeri2020{]}. An alpha level of 0.05 was used for the statistical tests.

@@

Teachers' average heart rate during the entire course of the study was approximately 96.26 bpm with a standard deviation of 14.22 and a range from 56 to 139 bpm.

@@

\hypertarget{pairwaise-t-test-and-effect-size}{%
\subsubsection{Pairwaise t-test and effect size}\label{pairwaise-t-test-and-effect-size}}

@@

\hypertarget{first-visual-results}{%
\section{First visual results}\label{first-visual-results}}

The graph @ref(fig:overall\_plot) show the heart rate for the entire course of the study.

\includegraphics{fitbit_paper_files/figure-latex/overall_plot-1.pdf}

The second graph @ref(fig:phase\_plot) show the heart rate for the individual five phases.

\includegraphics{fitbit_paper_files/figure-latex/phase_plot-1.pdf}

@@

\leavevmode\vadjust pre{\hypertarget{ref-R-xfun}{}}%
Xie, Y. (2022). \emph{Xfun: Supporting functions for packages maintained by 'yihui xie'}. Retrieved from \url{https://CRAN.R-project.org/package=xfun}
